Calorinator: an interactive floor game to maintain body fitness

### 2015-02-06 paper.tex
change title etc

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
  pdftitle={Fitness Adventure: an interactive floor game to maintain body fitness},
  pdfauthor={LaTeX},
  pdfkeywords={HCI, fitness, floor, adventure},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=black,
  breaklinks=true,
}

@@

  \title{Fitness Adventure: an interactive floor game to maintain body fitness}

@@

  \subsection{Do not just copy existing solution to floor apps} % (fold)
  \label{sub:do_not_just_copy_existing_solution_to_floor_apps}

>>>>

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
  pdftitle={Calorinator: an interactive floor game to maintain body fitness},
  pdfauthor={LaTeX},
  pdfkeywords={HCI, fitness, floor, adventure},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=black,
  breaklinks=true,
}

@@

  \title{Calorinator: an interactive floor game to maintain body fitness}

@@

  \subsection{Do not just copy existing solutions to floor apps} % (fold)
  \label{sub:do_not_just_copy_existing_solution_to_floor_apps}
